Dismal Code: Studying the Evolution of Security Bugs

### 2013-06-26 docs/evol.tex
trying to make some space adjustments with no luck
paper size changes
fixed layout
content is ready

\begin{figure*}[t]
	\centering
	\includegraphics[scale=0.45]{version_count.pdf}
	\caption{Distribution of Version Count Among Project Population}
	\label{fig:version-count}
\end{figure*}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[scale=0.45]{bug_percent}
	\caption{Bug Percentage in Maven Repository}
	\label{fig:bug-per} 
\end{figure*}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.35]{bugsversionscorr}
  \caption{Histograms of correlations between bug counts and version
    ordinals per project. In brackets the total population size and
    the number of no correlation instances.}
  \label{fig:bugsversionscorr}
\end{figure*}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=\textwidth]{bugdiffs}
  \caption{Changes in bug counts between versions.}
  \label{fig:bugdiffs}
\end{figure*}

@@

To examine the relation between the persistence of different kinds of
bugs, and of security bugs in particular, we used as a persistence
indicator the number of versions a bug remains open in a project. We
grouped the persistence numbers by bug categories and then performed a
Mann-Whitney $U$~\cite{HM98} test among all bug category pairs. The results are
presented in Table~\ref{tbl:bug_persistence}. Cells in brackets show
pairs where no statistically significant difference was found.

@@

@@

We explored the relation between defects with the size of a project
version, measured by the size of its {\sc jar} file by carrying out
correlation tests between the size and the defect counts for each
project and version. The results, all statistically significant ($p
\ll 0.05$) can be seen in Table~\ref{tbl:jarsizecorr}.  \textbf{The {\it
  Security High} category stands out by having a remarkably lower
effect than the other categories}, even {\it Security Low} that nearly
tops the list.

@@

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
Figure~\ref{fig:corrplot}. We found significant, but not always
strong, correlations between all pairs. In general, the {\it Security
  High} category showed the weakest correlations with the other
categories. Our results show that in general \textbf{bugs do flock together}.
We do not find projects with only a certain kind of bug; bugs come
upon projects in swarms of different kinds. Bugs of the {\it Security
  High} category, though, are different: they are either not
associated with other bugs, or only weakly so. Perhaps it takes a
special kind of blunder to make it a security hazard.

\begin{table}[t]
    \centering
    \caption{Correlation matrix}
    \label{tbl:corrmatrix}
    \input{corrmatrix.tex}
    \\
    \small The matrix presents pairwise correlations between the
        different bug categories.
\end{table}

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.6]{corrplot.pdf}
  \caption{Correlation matrix plot for bug categories}
  \label{fig:corrplot}
\end{figure*}

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.42]{version_count.pdf}
	\caption{Distribution of Version Count Among Project Population}
	\label{fig:version-count}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.39]{bug_percent}
	\caption{Bug Percentage in Maven Repository}
	\label{fig:bug-per} 
\end{figure}

@@

@@

\begin{figure*}[p]
  \centering
  \includegraphics[scale=0.30]{bugsversionscorr}
  \caption{Histograms of correlations between bug counts and version
    ordinals per project. In brackets the total population size and
    the number of no correlation instances.}
  \label{fig:bugsversionscorr}
  \centering
  \includegraphics[scale=0.35]{bugdiffs}
  \caption{Changes in bug counts between versions.}
  \label{fig:bugdiffs}
\end{figure*}

@@

To examine the relation between the persistence of different kinds of
bugs, and of security bugs in particular, we used as a persistence
indicator the number of versions a bug remains open in a project.
To ``tag" a bug we created a bug identifier by using
the type of the bug, the method name and the class name in which
the bug was found in. We chose not to use the line number
of the location of the bug since it could change from version
to version and after a possible code refactoring.
We grouped the persistence numbers by bug categories and then performed a
Mann-Whitney $U$~\cite{HM98} test among all bug category pairs. The results are
presented in Table~\ref{tbl:bug_persistence}. Cells in brackets show
pairs where no statistically significant difference was found.

@@

We explored the relation between defects with the size of a project
version, measured by the size of its {\sc jar} file by carrying out
correlation tests between the size and the defect counts for each
project and version. The results, all statistically significant ($p
\ll 0.05$) can be seen in Table~\ref{tbl:jarsizecorr}.  \textbf{The {\it
  Security High} category stands out by having a remarkably lower
effect than the other categories}, even {\it Security Low} that nearly
tops the list.
% dds proposed the following:
Given that, we could say that it would be productive to search for and fix
security bugs even if a project grows bigger.

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime. The results can be seen in % Table~\ref{tbl:corrmatrix} and
Figure~\ref{fig:corrplot}. We found significant, but not always
strong, correlations between all pairs. In general, the {\it Security
  High} category showed the weakest correlations with the other
categories. Our results show that in general \textbf{bugs do flock together}.
We do not find projects with only a certain kind of bug; bugs come
upon projects in swarms of different kinds. Bugs of the {\it Security
  High} category, though, are different: they are either not
associated with other bugs, or only weakly so. Perhaps it takes a
special kind of blunder to make it a security hazard.

%\begin{table*}[t]
%    \centering
%    \caption{Correlation matrix}
%    \label{tbl:corrmatrix}
%    \input{corrmatrix.tex}
%    \\
%    \small The matrix presents pairwise correlations between the
%        different bug categories.
%\end{table*}

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.47]{corrplot.pdf}
  \caption{Correlation matrix plot for bug categories}
  \label{fig:corrplot}
\end{figure}

@@

@@
